\documentclass[a4paper,9pt]{article}

\usepackage{fontspec} 					%for loading fonts
\usepackage{xunicode,xltxtra,url,parskip} 	%other packages for formatting
\RequirePackage{color,graphicx}
\usepackage{fontawesome}
\usepackage{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

\usepackage{enumitem}
\setlist{nolistsep}

\usepackage{geometry}
\geometry{
    a4paper,
    % total={170mm,257mm},
    left=10mm,
    right=10mm,
    top=15mm,
    bottom=15mm,
}

%CV Sections inspired by:
%http://stefano.italians.nl/archives/26
\usepackage{titlesec}
\titleformat{\section}{\bfseries\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{2pt}{2pt}

\begin{document}


\pagestyle{empty} % non-numbered pages

\par{
    \center
{\Huge SHIH-MING WANG}\\
\faEnvelope: \href{mailto:swang150@ucsc.edu}{swang150@ucsc.edu} \\
\faUser: \href{http://ipod825.github.io/}{http://ipod825.github.io/}\\
\faLinkedin: \href{https://www.linkedin.com/in/shih-ming-wang-73aa3769/}{https://www.linkedin.com/in/shih-ming-wang}\\
\bigskip\par}

%Section: Education
\section{Education}
    \textbf{M.S., Computer Science}, University of California, Santa Cruz \ (GPA:3.87/4.0)\hfill Sep. 2016-Present\\
    (Performed three years of studies in pursuit of Ph.D. before exiting program.)\\
    \textbf{M.S., Computer Science}, National Taiwan University \ (GPA:4.21/4.3)\hfill Sep. 2012 - June 2014 \\
    \textbf{B.S., Electrical Engineering}, National Taiwan University \hfill Sep. 2008 - June 2012


% \section{Coursework} Machine Learning, Advanced Machine Learning (graphical model), Artificial Intelligence, Optimization, Classical And Bayesian Inference, Image Analysis and Computer Vision, Analysis of Algorithms, Programming Languages

\section{Work Experience}
\textbf{Software Engineering Intern, Google Inc.}, Mountain View, USA \hfill Jun. 2019 - Sep. 2019 \par
\begin{itemize}
    \item \textbf{Android On-Device Video Intelligence - ML model evaluation and prototype}
    \begin{itemize}
        \item The project focused on building machine learning model and pipeline for the video intelligence project, aiming to provide high level attributes for videos with on-device machine learning model. Adopted SceneNet and built an video classification pipeline using MediaPipe. Evaluated the performance of the method on the public Youtube-8M dataset.
    \end{itemize}
\end{itemize}
\textbf{Software Engineering Intern, Google Inc.}, Boulder, USA \hfill Jun. 2018 - Sep. 2016 \par
\begin{itemize}
    \item \textbf{HD Mapfacts Diff}
    \begin{itemize}
        \item The goal of the project was to detect wrongly labeled building polygons in Geo team's Mapfacts database with up-to-date aerial image. Trained the semantic segmentation model, deeplabV3+, using high-quality labels and designed a heuristic algorithm comparing model predictions and human labels to detect potential wrong labels.
    \end{itemize}
\end{itemize}
\section{Research Experience}
\textbf{Machine Learning Research Assistant, Academia Sinica}, Taipei, Taiwan \hfill Aug. 2015 - July 2016 \par
\begin{itemize}
    \item \textbf{Lightweight Discourse CNN Model for Sentiment Analysis}
    \begin{itemize}
        \item Proposed a new CNN model incorporating the knowledge of discourse rules (e.g contrast and concession) and the learning ability of the deep neural network.
        \item Performed experiments on several well-known sentiment analysis datasets (e.g. Stanford Sentiment Tree-bank) showing the simplicity and effectiveness of the proposed model.
    \end{itemize}
    \item \textbf{Sensing Emotions in Text Messages}
    \begin{itemize}
        \item Supervised on the project aiming to build a system that automatically conveys the emotion of received text to enrich the context in computer mediated communications.
        \item Built sentiment classifiers from LiveJournal posts with pre-trained word embedding as features.
    \end{itemize}

    \item \textbf{Augmented NTUSD}: Built a Chinese sentiment dictionary containing polarity information of words for use of research on sentiment analysis. Designed experiments to test the applicability of the dictionary.
\end{itemize}

% \faMapMarker~\textbf{National Taiwan University}, Graduate Research Assistant \hfill Sep. 2012 - June 2014 \par
% \textbf{Thesis}: Investigation on Optimal Mixing with Linkage Sets and Its Application \\
% \textbf{LTGA Improvement}: Analyzed on a theoretical basis how the linkage-tee genetic algorithm (LTGA) utilizes its linkage model and improved LTGA by applying a dynamic model throughout the optimizing process. \\
% \textbf{GA Benchmark Design}: Analyzed on a theoretical basis what problems are difficult for genetic algorithms (GA-hard) and designed a benchmark with controllable problem complexity for testing modern GAs.


% \section{ACHIEVEMENT \& AWARDS}
%
% \textbf{Fellowship}, University of California, Santa Cruz \hfill Jan. 2017 - Mar. 2017
%
% \textbf{Teaching Assistantship}, University of California, Santa Cruz \hfill Sep. 2016 - present
%
% \textbf{Travel Grant of Domestic Graduate Attending International Symposiums}, Ministry of Science and Technology, Taiwan \hfill Sep. 2014

% \textbf{Teaching Assistantship}, National Taiwan University \hfill Sep. 2013 - June 2014
% \begin{itemize}
%     \item Available to top 10\% of graduate students.
% \end{itemize}


\section{Projects}
\href{https://github.com/ipod825/keraflow}{\textbf{Keraflow}}: Personal open source project implementing a deep learning library on top of \textbf{Theano} and \textbf{Tensorflow}. Redesigned the popular deep learning library Keras with the same utility but a simpler architecture aiming for easier development for package developers and clearer core dump for package users. \\
\href{https://github.com/ipod825/vim-netranger}{\textbf{vim-netranger}}: Personal open source project. A ranger-like system/cloud storage explorer plugin for Vim, bringing together the best of Vim, ranger, and rclone.  \\
% \textbf{Recommendation System on Yelp Data} Course project for the Machine Learning class (UCSC). Implemented using only \textbf{scipy} \& \textbf{numpy} a hybrid collaborative filtering model combining neighborhood model and factorization model, trained by batch gradient descent. \\
% \textbf{Chinese OCR}: Course project for the OCR contest in the Machine Learning class (NTU). Implemented algorithms including naieve Bayes, support vector machine, neural network. \\
% \textbf{ChenLianYen}(Javascript): Course project implementing a web-based RPG game, where the user can control the role to explore the map and attack monsters on the map. \\
% \textbf{Racing Beer}: Course project for Multimedia Lab (NTU). Implemented a 3D model \textbf{android} racing game. Multiple players can contest with each other through blue-tooth. Demo available on my personal web page. \\
% \textbf{Crazy Ants}: Course project for Multimedia Lab (NTU). Implemented an \textbf{ios} app game. Players use different weapons to destroy ant army. Demo available on my personal web page.


\section{Publication}
\textbf{Wang, S. M.}, \& Ku, L. W. (2016). ANTUSD: A Large Chinese Sentiment Dictionary.

\textbf{Wang, S. M.}, Tung, Y. F., \& Yu, T. L. (2014, July). Investigation on efficiency of optimal mixing on various linkage sets. In 2014 IEEE Congress on Evolutionary Computation (CEC) (pp. 2475-2482). IEEE.

\textbf{Wang, S. M.}, Wu, J. W., Chen, W. M., \& Yu, T. L. (2013, July). Design of test problems for discrete estimation of distribution algorithms. In Proceedings of the 15th annual conference on Genetic and evolutionary computation (pp. 407-414). ACM.

\section{Skills}
\textbf{Programming Language}: C/C++, Java, Python, R, Scala, Julia, MATLAB, Javascript \\
\textbf{Machine Learning Libraries}: scipy, scikit-learn, Stanford CoreNLP, tensorflow, pytorch, Keras \\
% \textbf{General}: zsh, git, neovim, gdb, pudb, pyenv \\
% \textbf{Foreign Languages}: Mandarin (native), Taiwanese (intermediate) \\

\end{document}
